On the power of oritatami cotranscriptional folding with unary bead sequence\thanks{This work is supported in part by KAKENHI Grant-in-Aid for Challenging Research (Exploratory) No.~18K19779 and JST Program to Disseminate Tenure Tracking System No.~6F36 granted to S.~Z.~F. and S.~S.}

### 2018-12-05 tt_theorem.tex
12/5 evening....

In order to prove this Tunnel Troll Theorem, we use the following three lemmas.
%Let us introduce some lemmas for proving Tunnel Troll Theorem.

@@

\begin{lemma}
\label{TTT_entrance_Tab}
Let $\Xi$ be a deterministic unary oritatami system at delay $\delta = 1$, arity $\alpha =2$. 
Assume $\Xi$ stabilizes the transcript until $w[i-1]$. If $S[i+1] = b$ and $S[i+2] \in \{ t_s, t_o \} $, then $\#bc(C_{i-1}) > \#bc(C_{i})$.
\end{lemma}

@@

\begin{lemma}
\label{TTT_tunnelC_lemma}
Let $\Xi$ be a deterministic unary oritatami system of delay $\delta = 1$, arity $\alpha = 2$.
If $S[i+2] = t_a$, the following statements hold.
\begin{enumerate}
\item If $w[i]$ forms at least one bond, $\#bc(C_{i-1}) > \#bc(C_{i+2})$.
\item If $w[i]$ does not consume any bond and $S[i] \in \{t_s, t_o \}$, $\#bc(C_{i-2}) > \#bc(C_{i+2})$.
\item If $w[i]$ does not consume any bond and $S[i] = t_a$, $\#bc(C_{i-3}) - 2 \geq \#bc(C_{i+2})$.
\end{enumerate}
%If there are indices $i,j$ such that $S[i..j+1]$ is either $bbt^{(j-i-1)}b$ and $S[i+2] = t_a$ or $bt^\ell bt^{j-i-1-\ell}b$ for some $\ell$ and $S[i+l+2] = t_a$, then $\#bc(C_{i-1}) > \#bc(C_j)$.
\end{lemma}

@@

\subsection{On structures provided by a unary and $\delta = 1$ oritatami system}

>>>>

In order to prove this theorem, we use the following three lemmas.
%Let us introduce some lemmas for proving Tunnel Troll Theorem.

@@

\begin{lemma}
\label{TTT_entrance_Tab}
Let $\Xi$ be a deterministic unary oritatami system at delay $\delta = 1$ and arity $\alpha =2$. 
Assume $\Xi$ stabilizes the transcript until $w[i-1]$. If $S[i+1] = b$ and $S[i+2] \in \{ t_s, t_o \} $, then $\#bc(C_{i-1}) > \#bc(C_{i})$.
\end{lemma}

@@

\begin{lemma}
\label{TTT_tunnelC_lemma}
Let $\Xi$ be a deterministic unary oritatami system of delay $\delta = 1$ and arity $\alpha = 2$.
If $S[i+2] = t_a$, the following statements hold.
\begin{enumerate}
\item If $w[i]$ forms at least one bond, $\#bc(C_{i-1}) > \#bc(C_{i+2})$.
\item If $w[i]$ does not consume any bond and $S[i] \in \{t_s, t_o \}$, $\#bc(C_{i-2}) > \#bc(C_{i+2})$.
\item If $w[i]$ does not consume any bond and $S[i] = t_a$, $\#bc(C_{i-3}) - 2 \geq \#bc(C_{i+2})$.
\end{enumerate}
%If there are indices $i,j$ such that $S[i..j+1]$ is either $bbt^{(j-i-1)}b$ and $S[i+2] = t_a$ or $bt^\ell bt^{j-i-1-\ell}b$ for some $\ell$ and $S[i+l+2] = t_a$, then $\#bc(C_{i-1}) > \#bc(C_j)$.
\end{lemma}

@@

\subsection{Upper bounds on the length of conformation foldable deterministically at delay $\delta = 1$.}
